Figures and Tables

### 2021-02-11 paper/figures_tables.Rmd
Finished figures in docx fortmat

---
title: "Figures and Tables"
subtitle: ' '
output:
  html_document:
    toc: yes
  word_document:
    toc: yes
bibliography: ../paper/mybibfile.bib
---

@@

ggplot() +
  geom_path(data = animalTraj, aes(x = xloc, y = yloc), size = 1, color = "darkgrey") +
  geom_point(data = animalTraj, aes(x = xloc, y = yloc), color = "black", size = 1) +
  geom_point(data = seed_loc, aes(x = xloc, y = yloc), color = "red", size = 3) +
  geom_point(aes(x = 0, y = 0), color = "black", size = 5)+
  geom_vline(aes(xintercept=0), linetype = "dotted") + geom_hline(aes(yintercept = 0), linetype = "dotted") +
  labs(x = "x", y = "y") +
  coord_fixed() +
  theme_bw() -> fig_traj

@@

```{r fig.width=2.5, fig.height=4}
plot_grid(fig_GRT, fig_MD, align = "v", nrow = 2, labels = "AUTO", label_size = 10)
```

@@

```{r fig.height=2, fig.width=6}
plot_grid(fig_traj, fig_disp, fig_agg, ncol = 3, align = "h", labels = "AUTO", label_size = 8)
```

@@

>>>>

---
title: "Figures and Tables"
subtitle: ' '
output:
  word_document:
    toc: yes
  html_document:
    toc: yes
bibliography: ../paper/mybibfile.bib
---

@@

ggplot() +
  geom_path(data = animalTraj, aes(x = xloc, y = yloc), size = 1, color = "darkgrey") +
  geom_point(data = animalTraj, aes(x = xloc, y = yloc), color = "black") +
  geom_point(data = seed_loc, aes(x = xloc, y = yloc), color = "red", size = 3) +
  geom_point(aes(x = 0, y = 0), color = "black", size = 5)+
  geom_vline(aes(xintercept=0), linetype = "dotted") + geom_hline(aes(yintercept = 0), linetype = "dotted") +
  labs(x = "x", y = "y") +
  coord_fixed() +
  theme_bw() -> fig_traj

@@

```{r fig.width=2.5, fig.height=4}
plot_grid(fig_GRT, fig_MD, align = "v", nrow = 2, labels = "AUTO", label_size = 10)

# ggsave("paper/figures/Figure1.png",
#        width = 2.5,
#        height = 4,
#        units = "in",
#        dpi = 300)
```

@@

```{r fig.height=2, fig.width=6}
plot_grid(fig_traj, fig_disp, fig_agg, ncol = 3, align = "h", labels = "AUTO", label_size = 8)

# ggsave("paper/figures/Figure2.png",
#        width = 6,
#        height = 2,
#        units = "in",
#        dpi = 300)
```

@@

# ggsave("paper/figures/Figure3.png",
#        width = 6,
#        height = 2.5,
#        units = "in",
#        dpi = 300)
